---
title: "Case_study_GUSTO"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
load_file=paste0(getwd(),"/../2021.08.26.RDS")

library(knitr)
knitr::opts_chunk$set(echo = TRUE)

load_results <- FALSE  #If true, will not run the simulation, rather will load the results
save_results <- TRUE
```

```{r echo=FALSE, message=FALSE}
source("case_study_GUSTO.R")
print("R code succesfully sourced.\n")
```

The model is 
```{r echo=FALSE} 
settings$master_formula 
```


```{r main, echo=FALSE, message=FALSE, dev='png', fig.show='hide', results=FALSE}
case_study_gusto(load_file=load_file)
```

```{r echo=FALSE}
print(sprintf("Number of simulaitons:%d",settings$n_sim))
```

## Regressoin table (Table 1)
```{r echo=FALSE, message=FALSE}
knitr::kable(results$table_1)
```



## Figures for the case study
## Decision curve
```{r echo=FALSE}
  print("Optimism-corrected (red) NB of the candidate model and its Bayesian estimators (orange: ordinary bootstrap, blue: Bayesian bootstrap), compared with the NB of treating all (black) and treating none (gray)")

  plot(results$res0[,'lambda'],results$res0[,'dc_model']-results$res0[,'optimism'],type='l',   xlab="Threshold", ylab="Net benefit", col="red", lwd=2)
  lines(results$res0[,'lambda'],results$res0[,'dc_all'],type='l',col="black")
  lines(results$res0[,'lambda'],results$res0[,'dc_all']*0,type='l',col="gray")
  lines(results$res0[,'lambda'],results$res0[,'NB_model'],type='l',col="orange" ,lwd=2)
  lines(results$res1[,'lambda'],results$res1[,'NB_model'],type='l',col="blue", lwd=2)
  #lines(tmp[,'lambda'],tmp[,'NB_model'],col="red")
```

### Ordinary bootstrap
```{r echo=FALSE, message=FALSE, results=FALSE}
process_results(results$res0,graphs=c('summit','voi'))
```

### Bayesian bootstrap
```{r echo=FALSE, message=FALSE, results=FALSE}
process_results(results$res1,graphs=c('summit','voi'))
```

##Numerical values of the case study
```{r echo=FALSE, message=FALSE}
print(sprintf("Optimism-corrected AUC:%.4f", results$auc[1]-results$auc[2]))

print(sprintf("Default threshold is: %f",settings$default_th))
  
produce <- function(res)
{
  x <- which(res[,'lambda']==settings$default_th)

  print(sprintf("Expected NB at default threshold without any model:%.4f",max(0,res[x,'NB_all'])))
  print(sprintf("INB of the proposed model at default threshold:%.4f",res[x,'NB_model']))
  print(sprintf("INB of the correct model at default threshold:%.4f",res[x,'NB_max']))
  print(sprintf("voi at default threshold:%.4f",res[x,'voi']))
  voi_r <- (res[x,'NB_max']-max(0,res[x,'NB_all']))/(res[x,'NB_model']-max(0,res[x,'NB_all']))
  print(sprintf("Relative voi at default threshold:%.4f", voi_r))
  
  area_under_inb_current <- mean(res[,'NB_model']-pmax(0,res[,'NB_all']))
  area_under_inb_perfect <- mean(res[,'NB_max']-pmax(0,res[,'NB_all']))
  print(sprintf("Area under INB curve with current information:%.4f", area_under_inb_current))
  print(sprintf("Area under INB curve with perfect information:%.4f", area_under_inb_perfect))
  global_voi_r <- area_under_inb_perfect/area_under_inb_current
  print(sprintf("Global relative voi:%.4f", global_voi_r))
}

print("Ordinary bootstrap:")
produce(results$res0)
print("Bayesian bootstrap:")
produce(results$res1)
```


### voi by sample size
```{r echo=FALSE}
data("gusto")
gusto$kill <- (as.numeric(gusto$Killip)>1)*1
results <- c()
set.seed(1234)
results$voi_by_sample_size <- voi_by_sample_size(1,settings$sample_sizes)

if(!is.null(results$voi_by_sample_size))
{
  if(length(settings$custom_th)==1){
  print("voi at index threshold")
  plot(results$voi_by_sample_size[,1:2],type='l', log='x', xlab="Sample size", ylab="EVPI", col='red', lwd=2)
  print("voi_r at index threshold")
  plot(results$voi_by_sample_size[,c(1,3)],type='l', log='x', xlab="Sample size", ylab="Relative EVPI", col='red', lwd=2)
  } else{
    require(ggplot2)
    require(tidyr)
    
    df_voi_th <- data.frame(sample=results$voi_by_sample_size[,1])
    df_voi_th <- cbind(df_voi_th,results$voi_by_sample_size[,grep("voi_th",colnames(results$voi_by_sample_size))])
    df_voi_r <- data.frame(sample=results$voi_by_sample_size[,1])
    df_voi_r <- cbind(df_voi_r,results$voi_by_sample_size[,grep("voi_r",colnames(results$voi_by_sample_size))])
    colnames(df_voi_th)[-1] <-  colnames(df_voi_r)[-1] <- settings$custom_th
    df_voi_th <- pivot_longer(df_voi_th,cols=-1,names_to='Threshold',values_to="EVPI")
    df_voi_r <- pivot_longer(df_voi_r,cols=-1,names_to='Threshold',values_to="EVPI")
    
    ggplot(data=df_voi_th,aes(x=sample,y=EVPI,color=Threshold)) +
      geom_line(size=1.5, alpha = 0.7) +
      theme_classic() +
      xlab("Sample size") +
      theme(legend.position = 'top')
    
    ggplot(data=df_voi_r,aes(x=sample,y=EVPI,color=Threshold)) +
      geom_line(size=1.5, alpha = 0.7) +
      theme_classic() +
      ylab("Relative EVPI") +
      xlab("Sample size") +
      theme(legend.position = 'top')
  }
}
```

### voi with full data
```{r echo=FALSE}
print(sprintf("voi at index threshold is: %.4f",results$voi_by_sample_size[dim(results$voi_by_sample_size)[1],2]))
print(sprintf("voi_r at index threshold is: %.4f",results$voi_by_sample_size[dim(results$voi_by_sample_size)[1],3]))
